Xor-Some Preregistered Study: Analyses

### 2021-12-20 analysis/main/03_xor-some_prereg_analysis_final.Rmd
full SD grid search vs Int

model_SI_posteriors_long %>%
  ggplot(.) + # 
  stat_halfeye(aes(y = effect, x = value, 
                   fill = stat(case_when(x %>% between(-0.05, 0.05) ~ "no effect", x < -0.05 ~ "negative effect", x > 0.05 ~ "positive effect"))
                   ), 
               alpha = .7) +
  geom_vline(xintercept = c(-.05, .05), linetype = "dashed") +
  scale_fill_manual(name = "Direction of effect", values = c("coral", "yellow3", "mediumseagreen")) +
  ggtitle("Posterior effect distributions. Points indicate posterior means\nThick lines indicate 66% CrIs, thin lines 95% CrIs.")

>>>>

model_SI_posteriors_long %>%
  mutate(effect = factor(effect, 
                         levels = c("relevance_xor", "relevance_some", "prior_xor", "prior_some", "competence_xor", "competence_some"), 
                         labels = c("Relevance (or)", "Relevance (some)", "Prior (or)", "Prior (some)", "Competence (or)", "Competence (some)"))) %>%
  ggplot(.) + # 
  stat_halfeye(aes(y = effect, x = value, 
                   fill = stat(case_when(x %>% between(-0.05, 0.05) ~ "no effect", x < -0.05 ~ "negative effect", x > 0.05 ~ "positive effect"))
                   ), 
               alpha = .7) +
  geom_vline(xintercept = c(-.05, .05), linetype = "dashed") +
  scale_fill_manual(name = "Direction of effect", values = c("coral", "yellow3", "mediumseagreen")) +
  labs(x = "Effect size", y = "Effect") +
  theme(legend.position = "top",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        axis.title = element_text(size = 13),
        strip.text.x = element_text(size = 13),
        strip.text.y = element_text(size = 13))

ggsave("../../writing/ELM2/posterior-effects.pdf", width=7, height=5)
```

### 2021-12-20 analysis/main/05_xor-some_analysis_model_compariso_grid-search-SD.Rmd
full SD grid search vs Int

>>>>

## Model comparisons with grid search for final paper
Below, we conduct a similar grid search over more models. More specifically, we compute the BF in favor of a more complex model over the intercept-only baseline model. We compute these pairwise comparisons for each iteratively added explaantory factor. This results in 7 model comparisons. For each comparison, we perform a small grid search over the SD parameter of the prior t-distribution over the fixed effects regression coefficients, using the values [0.05, 0.1, 0.15]. For each model, 40.000 samples are extracted.
```{r}
# define a convenience function for iterating over the SDs and critical models
models_grid_search_SD_full = function(sd_vec, iter, trigger) {
  # create output df
  results <- tribble(
    ~"model in favor", ~"model against", "~trigger", ~"SD", ~"BF"
  )
  # filter data by trigger
  data <- d_critical_zScored_wide %>% filter(main_type == trigger)
  # set priors
  for (i in sd_vec) {
    dist <- paste("student_t(1, 0, ", i, ")", sep = "")
    prior <- set_prior(dist, class = "b")
    # fit the baseline intercept only model with same prior SD
    prior_int <- set_prior(dist, class = "Intercept")
    model_int <- brm(target ~ 1 +
                   (1 | submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior_int,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    # fit the single predictor models
    model_pri <- brm(target ~ prior + 
                   (1 + prior || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    model_rel <- brm(target ~ relevance + 
                   (1 + relevance || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    model_comp <- brm(target ~ competence + 
                   (1 + competence || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    # fit rel * comp model with specific prior
    model_rel_comp <- brm(target ~ relevance*competence +
                   (1 + relevance + competence || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    # fit prior * comp model with specific prior
    model_pri_comp <- brm(target ~ prior*competence +
                   (1 + prior + competence || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    # rel*pri model
    model_rel_pri <- brm(target ~ prior*relevance +
                   (1 + prior + relevance || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    # fit full model
    model_pri_rel_comp <- brm(target ~ prior*competence*relevance +
                   (1 + prior + competence + relevance || submission_id) +
                   (1 | title),
                 data = data,
                 prior = prior,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = iter,
                 save_all_pars = TRUE
                 )
    # compute BF
    # iterate over list of models 
    model_list <- c("model_rel", "model_pri", "model_comp", "model_rel_comp", "model_pri_comp", "model_rel_pri", "model_pri_rel_comp")
    for (m in model_list) {
      bf <- bayes_factor(m, model_int, silent = TRUE)
      print(paste("SD: ", i, sep=""))
      print(paste("Model in favor: ", m, sep=""))
      print(paste("BF: ", bf, sep=""))
      # append to results dataframe, write out
      results <- results %>% add_row(
        "model in favor" = m,
        "model against" = "Int",
        "trigger" = trigger,
        SD = i,
        BF = round(bf[1]$bf, 4)
      )
    write_csv(results, 
              paste("../../data/main/grid_full_", trigger, "_SD_0_", i*100, ".csv", sep = ""))
    }

  }
  return (results)
}
```

```{r}
# call the grid search for xor 
grid_results_full_xor <- models_grid_search_SD_full(c(0.05, 0.1, 0.15), 40000, "xor")

# call the grid search for some 
grid_results_full_some <- models_grid_search_SD_full(c(0.05, 0.1, 0.15), 40000, "some")

# write out results
write_csv(grid_results_full_xor, "../../data/main/grid_full_xor_SD_final.csv")
write_csv(grid_results_full_some, "../../data/main/grid_full_some_SD_final.csv")

Plot the effect of SD against the BF:
```{r}
grid_results_full_xor <- read_csv("../../data/main/grid_full_xor_SD_final.csv")
grid_results_full_some <- read_csv("../../data/main/grid_full_some_SD_final.csv")
grid_results_both <- rbind(grid_results_full_xor, grid_results_full_some)

grid_results_both %>%
ggplot(., aes(x = SD, y = BF, color = `model in favor`)) +
  geom_point() +
  geom_line() +
  facet_wrap(~trigger) + 
  ggtitle("BF in favor of including a relevance effect over\n including a prior effect, depending on SD of prior t-distribution")

#ggsave("BF_vs_SD_all_vs_int.pdf", width = 8, height = 4)
```

```{r}

# bf <- bayes_factor(model_rel_comp, model_prior_comp, silent = TRUE)
#     print(paste("SD: ", i, sep=""))
#     print(paste("BF: ", bf, sep=""))
#     # append to results dataframe, write out
#     results <- results %>% add_row(
#       "model in favor" = "Rel * Comp",
#       "model against" = "Prior * Comp",
#       SD = i,
#       BF = round(bf[1]$bf, 4)
#     )
#     # dot might be a problem
#     write_csv(results, 
#               paste("../../data/main/grid_rel-pri_SD_0_", i*100, ".csv", sep = ""))
```
